A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-06 paper/elsarticle/elsarticle-template.tex
paper

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the camera, giving a virtual camera likewise facing directly downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Moreover, the virtual projector's axes are aligned with the axes of an image of the scene acquired by a camera, enabling intuitive placement of augmentations in the scene, in accordance with the placement of the camera.

@@

We evaluate our approach by considering the relative merits of augmenting 15 locations across the floorspace at the Pilotfabrik using our approach and two variants of a baseline approach. At each of the 15 locations, we aim to place an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions, with the horizontal axis of the image as projected to the floor measuring 30 cm.

 We carry out all steps of our approach within 15 minutes, which we set Our baseline in both instances calls for using the software bundled with the steerable mirror system mounted alongside our projector

>>>>

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the camera, giving a virtual camera likewise facing directly downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions.

Owing to the manner in which we place the virtual projector, the virtual projector's axes and thus the augmentation are aligned with the axes of an image of the scene acquired by a camera, enabling intuitive placement of augmentations in the scene in accordance with the placement of the camera. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that the center of the projector's image plane remains invariant to projective distortion, i.e., a steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, further facilitating placement.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik using our approach and two variants of a baseline approach. At each of the 15 locations, we aim to place an image aligned with the principal axes of the floorspace and such that the image appear in each instance to be free of projective distortions and to have the same dimensions, with the horizontal axis of the image as projected to the floor measuring 30 cm. We managed to carry out all steps using our approach within a time budget of 15 min. The first variant of the baseline approach is to carry out a manual keystone correction using the software bundled with the steerable mirror system mounted alongside our projector within the same 15 min time budget; we then compare the quality of the augmentations produced with this baseline with those produced using out approach. The second variant of the baseline approach is to record how much time is necessary to produce augmentations within a tolerance of what is desired.
